---
title: "Results Summary"
author: "Justin Priest"
date: "6/4/2019"
output: html_document
---

******

```{r imports, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(here)
library(extrafont)
# font_import()  #this only needs to be run once
loadfonts(device="win") #change for mac users


# Import analysis script (which calls data import)
source(here::here("code/cohoage_3_Analysis.R"))

#formatting numbers function
digform <- function(x, d = 2) sprintf(paste0("%1.", d, "f"), x) 

```


# Summary Stats:
```{r summaries, echo=FALSE, include=FALSE}
knitr::knit_hooks$set(inline = function(x) { if(!is.numeric(x)){ x }else{ prettyNum(round(x,2), big.mark=",") } })
options(digits = 2)

bernersnum <- nrow(coho_scales_berners)
bernersages <- coho_scales_berners %>% group_by(Age) %>% tally()



hughsmithnum <- nrow(coho_scales_hughsmith)
hughsmithages <- coho_scales_hughsmith %>% group_by(Age) %>% tally()


```
In total there were `r bernersnum + hughsmithnum` coho salmon analyzed. 

There were `r bernersnum` coho salmon from Berners River. 
Of these, there were `r (bernersages %>% filter(Age==1))[,2]` Age 1 fish 
(`r digform(100 * ((bernersages %>% filter(Age==1))[,2] / bernersnum), 1)`%), 
and `r (bernersages %>% filter(Age==2))[,2]` Age 2 fish
(`r digform(100 * ((bernersages %>% filter(Age==2))[,2] / bernersnum), 1)`%).

From Hugh Smith Lake there were `r hughsmithnum` coho salmon. 
Of these, there were `r (hughsmithages %>% filter(Age==1))[,2]` Age 1 fish
(`r digform(100 * ((hughsmithages %>% filter(Age==1))[,2] / hughsmithnum), 1)`%), 
and `r (hughsmithages %>% filter(Age==2))[,2]` Age 2 fish
(`r digform(100 * ((hughsmithages %>% filter(Age==2))[,2] / hughsmithnum), 1)`%).



```{r newsect, echo=FALSE}


```

