---
title: "Results Summary"
author: "Justin Priest"
date: "6/4/2019"
output: html_document
---

******

```{r imports, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(here)
library(ggridges)
library(extrafont)
# font_import()  #this only needs to be run once
loadfonts(device="win") #change for mac users


# Import analysis script (which calls data import)
source(here::here("code/cohoage_3_Analysis.R"))

#formatting numbers function
digform <- function(x, d = 2) sprintf(paste0("%1.", d, "f"), x) 

```


# Summary Stats:
```{r summaries, echo=FALSE, include=FALSE}
knitr::knit_hooks$set(inline = function(x) { if(!is.numeric(x)){ x }else{ prettyNum(round(x,2), big.mark=",") } })
options(digits = 2)

bernersnum <- nrow(coho_scales_berners)
bernersages <- coho_scales_berners %>% group_by(Age) %>% tally()



hughsmithnum <- nrow(coho_scales_hughsmith)
hughsmithages <- coho_scales_hughsmith %>% group_by(Age) %>% tally()


```
In total there were `r bernersnum + hughsmithnum` coho salmon analyzed. 

There were `r bernersnum` coho salmon from Berners River. 
Of these, there were `r (bernersages %>% filter(Age==1))[,2]` Age 1 fish 
(`r digform(100 * ((bernersages %>% filter(Age==1))[,2] / bernersnum), 1)`%), 
and `r (bernersages %>% filter(Age==2))[,2]` Age 2 fish
(`r digform(100 * ((bernersages %>% filter(Age==2))[,2] / bernersnum), 1)`%).

From Hugh Smith Lake there were `r hughsmithnum` coho salmon. 
Of these, there were `r (hughsmithages %>% filter(Age==1))[,2]` Age 1 fish
(`r digform(100 * ((hughsmithages %>% filter(Age==1))[,2] / hughsmithnum), 1)`%), 
and `r (hughsmithages %>% filter(Age==2))[,2]` Age 2 fish
(`r digform(100 * ((hughsmithages %>% filter(Age==2))[,2] / hughsmithnum), 1)`%).


```{r correlations, echo=FALSE, message=FALSE, warning=FALSE}
cor.test(coho_scales_berners$Q2, coho_scales_berners$Q9abs)
cor.test(coho_scales_hughsmith$Q2, coho_scales_hughsmith$Q9abs)



```


```{r ridgeplots, echo=FALSE, message=FALSE, warning=FALSE}

ggplot(coho_scales_berners, aes(x = Q2, y = fct_rev(as.factor(Year)))) +
  geom_density_ridges(aes(fill = as.factor(Age)), scale = 2, alpha = 0.8) + theme_ridges(center_axis_labels = TRUE) +
  scale_fill_manual(values = c("#d1d1d1", "#606060"), guide = FALSE) +
  annotate("text", x = 0.19, y="2005", vjust = -0.5, label="Age 1", family="Times New Roman", colour="black") +
  annotate("text", x = 0.35, y="2005", vjust = -0.5, label="Age 2", family="Times New Roman", colour="black") +
  ggtitle("A) Berners River")+ xlab ("Distance Circulus 3–Scale Edge (mm)") + ylab("Year") +
  theme(text=element_text(family="Times New Roman", size=12)) -> bernersQ2_ridge


ggplot(coho_scales_hughsmith, aes(x = Q2, y = fct_rev(as.factor(Year)))) +
  geom_density_ridges(aes(fill = as.factor(Age)), scale = 2, alpha = 0.8) + theme_ridges(center_axis_labels = TRUE) +
  scale_fill_manual(values = c("#d1d1d1", "#606060"), guide = FALSE) +
  scale_y_discrete(expand = expand_scale(add = c(0.5, 3))) +
  annotate("text", x = 0.3, y="2005", vjust = -0.5, label="Age 1", family="Times New Roman", colour="black") +
  annotate("text", x = 0.45, y="2005", vjust = -0.5, label="Age 2", family="Times New Roman", colour="black") +
  ggtitle("B) Hugh Smith Lake")+ xlab ("Distance Circulus 3–Scale Edge (mm)") + ylab("Year") +
  theme(text=element_text(family="Times New Roman", size=12)) -> hughsmithQ2_ridge


cowplot::plot_grid(bernersQ2_ridge, hughsmithQ2_ridge, align = "h", nrow = 1, ncol=2) 
#ggsave("figures/Q2_ridgeplot.png", dpi = 500, height = 4 , width = 6, units = "in")





ggplot(coho_scales_berners, aes(x = Q9abs, y = fct_rev(as.factor(Year)))) +
  geom_density_ridges(aes(fill = as.factor(Age)), scale = 2, alpha = 0.8) + theme_ridges(center_axis_labels = TRUE) +
  scale_fill_manual(values = c("#d1d1d1", "#606060"), guide = FALSE) +
  ggtitle("C) Berners River")+ xlab ("Distance Circulus 3–Circulus 8 (mm)") + ylab("Year") +
  theme(text=element_text(family="Times New Roman", size=12)) -> bernersQ9_ridge


ggplot(coho_scales_hughsmith, aes(x = Q9abs, y = fct_rev(as.factor(Year)))) +
  geom_density_ridges(aes(fill = as.factor(Age)), scale = 2, alpha = 0.8) + theme_ridges(center_axis_labels = TRUE) +
  scale_fill_manual(values = c("#d1d1d1", "#606060")) +
  scale_y_discrete(expand = expand_scale(add = c(0.6, 2.65))) +
  labs(fill = "Age") +
  ggtitle("D) Hugh Smith Lake")+ xlab ("Distance Circulus 3–Circulus 8 (mm)") + ylab("Year") +
  theme(text=element_text(family="Times New Roman", size=12)) -> hughsmithQ9_ridge


cowplot::plot_grid(bernersQ9_ridge, hughsmithQ9_ridge, align = "h", nrow = 1, ncol=2) 
#ggsave("figures/Q9_ridgeplot.png", dpi = 500, height = 4 , width = 6, units = "in")



```

